---
title: "Presentation with plotly"
author: "Bram van Dam"
date: "July 25, 2017"
output: 
  ioslides_presentation: 
    keep_md: yes
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code.r{
  font-size: 10px;
}
pre {
  font-size: 14px
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This is an R Markdown presentation for the course "Developing data products", which is part of the Data science specialization on Coursera (https://www.coursera.org/specializations/jhu-data-science/).

The next three slides contain:  
- Some background of the plot  
- The plotly plot  
- The code for the plot  

From my own testing, the plot does show up correctly in Microsoft Edge or Internet Explorer; the plot is not evaluated well with Firefox. So please use another browser if the plot doesn't show up.

## Background of plot

A dataset which can be found in any R installation is used. See http://stat.ethz.ch/R-manual/R-patched/library/datasets/html/state.html for more background on the data set.

On the following slide, the life expectancy (in years) is plotted against income per capita and the percentage of high-school graduates. Markers are colored by the murder rate per 100,000 population.  

By no way is any connection suggested, it just shows what kind of plots can be made with the plotly package in R.

## Plotly plot

```{r plot, ref.label = 'code', echo = FALSE, message = FALSE, warning = FALSE}

```


## R Code for the plot

```{r code, echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE}
library(plotly); library(datasets)
sdf <- as.data.frame(state.x77)

mstyle = list(color = ~`Murder`,
              colorscale = c('#FFE1A1', '#683531'),
              showscale = TRUE,
              colorbar = list(x = 0.8, y = 0.5, yanchor = "middle",
                              title = "Murder rate per\n 100,000 population"))
plot_ly(sdf, x = ~`Income`, y = ~`HS Grad`, z = ~`Life Exp`,
        type = "scatter3d",
        showlegend = FALSE,
        mode = "markers",
        marker = mstyle) %>%
    layout(title = "Life expectancy to income and high-school graduation",
           scene = list(xaxis = list(title = 'Income (per capita)'),
                        yaxis = list(title = 'High-school Graduates (%)'),
                        zaxis = list(title = 'Life expectancy (years)'))
           )
```
